### 2015-06-01 writing/SNLI paper/entailment_eval.tex
Clarification (I think)

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\hspace{-1.2em}\b{Our corpus}} & \b{SICK}\\
 & \t{Train} & \t{Test} & \t{Test}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \b{77.3} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} & \t{74.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} & \t{69.4}\\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy, training and testing on either our data or SICK, including models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%

>>>>

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\hspace{-1.2em}\b{Our corpus}} & \b{SICK}\\
 & \t{Train} & \t{Test} & \t{Test}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \b{77.3} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} & \t{74.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} & \t{69.4}\\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy, training on either our data or SICK, including models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%
